A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
introduce half-edge datastructure

\begin{figure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_shape_decomposition.pdf}
\caption{Simple case}
\label{shape_decomposition_simple}
\end{subfigure}
\begin{subfigure}{0.65\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_VD_VQ.pdf}
\caption{Complex case employing discretization}
\label{shape_decomp_complex}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
}
\label{skeletonization_comparison}
\end{figure}

@@

\subsubsection{Skeletal trapezoidation}
We employ a shape decomposition proposed by \citeauthor{Ding2016a} which starts from the medial axis and further decomposes the outline shape into simple fragments. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
See \cref{shape_decomposition_simple}.

>>>>

\begin{figure}
\begin{subfigure}{0.3\columnwidth}
\centering
%\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_shape_decomposition.pdf}
\includegraphics[height=1.5\columnwidth]{sources/method/half_edge_datastructure.pdf}
\caption{Simple case}
\label{shape_decomposition_simple}
\end{subfigure}
\begin{subfigure}{0.65\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_VD_VQ.pdf}
\caption{Complex case employing discretization}
\label{shape_decomp_complex}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
}
\label{skeletonization_comparison}
\end{figure}

@@

\subsubsection{Skeletal trapezoidation}
We employ a shape decomposition proposed by \citeauthor{Ding2016a} which starts from the medial axis and further decomposes the outline shape into simple fragments. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
We repesent such a skeleton in a standard half-edge datastructure.
See \cref{shape_decomposition_simple}.
